Opportunities for improvement in the care of adult trauma patients arriving

### 2024-11-29 manuscript.Rmd
flyttade på ATLS tabellen

(See Table \@ref(tab:atls) [@noauthor_atls_2018])

@@

The patients will be classified to different degrees of shock in parallel and separately, once with systolic blood pressure (SBP) and once with base excess (BE), regardless of their cause of shock. Based on these two parameters, the patients will be classified into four classes roughly based on the ATLS trauma shock classifications.

>>>>

@@

The patients will be classified to different degrees of shock in parallel and separately, once with systolic blood pressure (SBP) and once with base excess (BE), regardless of their cause of shock. Based on these two parameters, the patients will be classified into four classes roughly based on the ATLS trauma shock classifications (See Table \@ref(tab:atls) [@noauthor_atls_2018]).
